%=======================================================================
% File         : _intro.tex
% Title        : 
% Author(s)    : Sebastien VARRETTE <Sebastien.Varrette@uni.lu>
% Creation     : 06 Jul 2009
% Time-stamp:    <2009-07-15 15:29:41 svarrette>
% $Id: _intro.tex 447 2009-07-15 13:36:11Z svarrette $
%  
%   Copyright (c) 2009 Sebastien Varrette. 
%
% Licence: Creative Commons Attribution-Noncommercial-Share Alike 2.0 France
%
% You are free:
%   - to Share:  to copy, distribute and transmit the work
%   - to Remix: to adapt the work
%
% Under the following conditions:
%   - Attribution : You must attribute the work in the manner specified by the
%                   author or licensor (but  not in any way that suggests that
%                   they endorse you or your use of the work).  
%   - Noncommercial:  You may not use this work for commercial purposes.
%   - Share Alike: If you alter, transform, or build upon this work, you may
%                  distribute the resulting work only under the same or similar
%                  license to this one. 
%
% With the understanding that:
%   - Waiver: Any of the above conditions can be waived if you get permission from
%             the copyright holder. 
%   - Other Rights: In no way are any of the following rights affected by the
%                   license:  
%                    * Your fair dealing or fair use rights;
%                    * Apart from the remix rights granted under this license,
%                      the author's moral rights; 
%                     * Rights other persons may have either in the work itself
%                       or in how the work is used, such as publicity or privacy
%                       rights. 
%   - Notice:  For any reuse or distribution, you must make clear to others the
%              license terms of this work. The best way to do this is with a
%              link to this web page. 
%=======================================================================

Urban Terror (UrT for short) started as a realism mod for Quake III Arena,
reusing most of the concepts of the famous game Counterstrike~\cite{cs}.
The approach is similar to the one proposed by the Tactical Ops\footnote{See
\url{http://www.tactical-ops.de/}} mod for Unreal Tournament.
Yet with the release of the Quake III engine as an open-source software (through
the \texttt{ioquake3} project~\cite{ioq3}), Urban Terror is now completely free,
stand-alone (\emph{i.e.} it does not require to buy a copy of Quake III Arena)
and, more importantly, cross-platform so it can run on Windows \windows, Linux
\linux\ and Mac OS X \macosx.    
\\
The software package in itself comes with two elements: 
\begin{enumerate}\setitemsep
\item the client executable \texttt{ioUrbanTerror} for playing on a remote
  dedicated server. It is also possible to start a server at the same time you
  play to host a game and let other player join your game other the network;
\item a dedicated server executable \texttt{ioUrTded}.
\end{enumerate}

Whereas the UrT client can start a server, you have  access in this case to
limited functionality (in particular no votes) and performances (as your machine
also have to handle the graphics of your own game in addition to the server
tasks), which justify the configuration of a dedicated server. \\

This guide is based on my own experience to share information about the
configuration of a dedicated server for Urban Terror over a Linux machine
(hosting a Debian distribution).
I also detail the configuration of Big Brother Bot, a powerful and flexible
server administration package for online games which support in particular UrT. 
It permits the use of various plugins, in particular \texttt{xlrstats}, which
give access to statistics to the players of your server. 
The configuration of such plugins is also addressed by this document. \\

This document is not meant to be a reference guide (for this, just consider the
official manuals that come with each package), I just found it would be
interesting to centralize in a single document my notes for configuring each
elements. 
It is released under the terms of the CC licence Creative Commons
\emph{Attribution-Noncommercial-Share Alike} 2.0 France, hoping other persons
will help me to improve this document. \\
Your help, comments and feedback will be greatly appreciated ! Kindly address
them by mail at \url{Sebastien.Varrette@uni.lu}. 
The \LaTeX\ sources of this tutorial can also be obtained, as soon as you
ask them by mail at the same address. 

\paragraph{Writing conventions.}

When editing this document, I used several writing conventions summarized here: 
\begin{itemize}
\item An item preceded by an OS symbol (\windows, \linux\ or \macosx) qualify
  information specific to this OS; 
\item Command-lines are provided in a dedicated environment (grey boxes)
  prefixed by a prompt. 
  This prompt can be of two types: 
  \begin{enumerate}
  \item 
    \begin{lstlisting}[style=command]
 [user@host]>
    \end{lstlisting}
    This qualify a command that can be run with the rights of a normal user.
  \item
    \begin{lstlisting}[style=command]
 [root@host]#
    \end{lstlisting}
    This refers to a command to be run with superuser right (aka \texttt{root})
    - use \texttt{su} or \texttt{sudo} commands to switch to this mod
    eventually (see the man pages for more information).
  \end{enumerate}
Remember that this prompt is of course not part of the command provided. 
\end{itemize}

\paragraph{Organization.}

This tutorial is organized as follows: 
\S\ref{sec:urt_client} details the installation of the client software provided
by the Urban Terror package. Information for all OS are given and a brief
summary of some common game techniques are provided. 
Some advanced customization tricks (by adapting the \texttt{q3config.cfg} file)
are also given.  
Then \S\ref{sec:urt_server} expounds the configuration of a running dedicated
server for Urban Terror on a Linux machine. In particular, some useful scripts
(for instance to start/stop the server) are proposed. 
\S\ref{sec:b3} is dedicated to Big Brother Bot (B3). At this level, the
configuration of several plugins (\texttt{xlrstats} for instance) is detailed.  

\paragraph{Online repository.}

The latest version of this document is available on my personal web site 
\url{http://varrette.gforge.uni.lu/q3ut4/urt_setup.pdf}\\
The scripts provided in the appendix are available for download at the following url: 
\url{http://varrette.gforge.uni.lu/q3ut4/ConfigFiles/}\\

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% eof
%
% Local Variables:
% fill-column: 80
% mode: latex
% mode: flyspell
% mode: auto-fill
% End:
